Study protocol

### 2021-12-23 Manuscript/S1.Protocol.Rmd
updated given changes in the framework

# The last annotation file and posterior sample matrix in the session are found;
# the most predictive terms (based on the importance score) are chosen and
# simple prediction trees are used to map the terms to a random subset of the
# posterior probabilities (extracted from the posterior sample matrix saved
# during the last CR iteration). The score threshold and the number of trees can
# be chosen by the user; less stringent values can greatly increase computation
# time;

@@

selection_set_file <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx')

>>>>

# The last annotation file and posterior sample matrix in the session are found;
# the most predictive terms (based on the importance score) are chosen and
# simple prediction trees are used to map the terms to a random subset of the
# posterior probabilities (extracted from the posterior sample matrix saved
# during the last CR iteration). The score threshold and the number of trees can
# be chosen by the user; less stringent values can greatly increase computation
# time. By default results will be saved in file called rule_data.rds in the
# session folder.

@@

# No default is given for the save file, since generate_rule_selection_set()
# have no info about the session it's working on.
selection_set_file <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx')
